Achieving maximum possible precision on stellar radial-velocity measurements in multi-epoch spectroscopy

### 2017-12-01 paper/paper.tex
more background in intro

While the general idea of measuring a Doppler shift by the relative motions of stellar absorption lines is fairly straightforward, there are considerable subtleties to implementing this, from the choice of reference spectrum or template to the treatment of telluric absorption features. Ultra-stabilized spectrographs like HARPS \todo{(define \& cite)} predominantly utilize a cross-correlation method with a custom-built list of spectral lines (see e.g. ...).

[summary of the ways people derive precise \RV s from spectra; citations to binary mask papers, papers that compare template matching to binary masks]

We begin in Section \ref{s:info} with a derivation of the information-theory-based limit on the RV information content of a spectrum. In Section \ref{s:methods}, we summarize common RV extraction practices used by current \RV\ pipelines, including cross-correlation and template fitting. We then implement these techniques to extract \RV s using 5-\r{A} section of simulated and real spectra, as described in Section {s:data}. We compare the relative performances of the methods in Section \ref{s:experiments} and conclude with some recommendations for future RV pipelines in Section {s:summary}.

@@

\section{Summary \& Discussion}
\section{s:summary}

>>>>

While the general idea of measuring a Doppler shift by the relative motions of stellar absorption lines is fairly straightforward, there are considerable subtleties to implementing this, from the choice of reference spectrum or template to the treatment of telluric absorption features. Ultra-stabilized spectrographs like HARPS \todo{(define \& cite)} predominantly utilize a cross-correlation method with a custom-built list of spectral lines (see e.g. Queloz1995, Baranne1996). A lesser-used alternative is cross-correlation or maximum-likelihood fitting using a template spectrum generated from the data (Buchhave, Anglada-Escude). This often involves masking or downweighting of the most telluric-contaminated spectral regions.

On the other hand, gas-cell-calibrated spectrographs like HIRES and [whatever the McDonald one is] commonly adopt a more comprehensive forward-modeling approach. In this framework, the instrumental line spread function, the stellar RV, and other parameters are optimized by modeling each observation as a combination of shifted and instrument-convolved template spectra for the star and gas cell. [say a bit more]

Our primary aim in this work is to establish a common frame of reference for these methods based on their relative ability to extract maximum-precision RVs and their robustness in the face of various expected structured noise sources.

We begin in Section \ref{s:info} with a derivation of the information-theory-based limit on the RV information content of a spectrum. In Section \ref{s:methods}, we summarize common RV extraction practices used by current \RV\ pipelines, including cross-correlation and template fitting. We then implement these techniques to extract \RV s using 5-\r{A} section of simulated and real spectra, as described in Section \ref{s:data}. We compare the relative performances of the methods in Section \ref{s:experiments} and conclude with some recommendations for future RV pipelines in Section \ref{s:summary}.

@@

\section{Summary \& Discussion}
\label{s:summary}
